---
title: "Introduction to pedMermaid"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to pedMermaid}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pedMermaid)
```

[Markdown](https://www.markdownguide.org/) is a popular lightweight markup language that allows users to write using plain text, while adding various formatting to the text.
It is widely used for writing web content, blogging, documentation, reporting, and presentation.
It is supported on popular platforms such as [GitHub](https://github.com/), and popular file formats such as [R Markdown](https://rmarkdown.rstudio.com/), where markdown text, R code and outputs are collated.

[Mermaid](https://mermaid.js.org/) syntax is a Markdown-inspired text definition for creating dynamic and reproducible diagrams and charts.
It can be viewed in Mermaid editors or embedded and rendered in a Markdown or R Markdown document.
R package pedMermaid generates Mermaid syntax for creating a pedigree flowchart in Markdown and R Markdown, from a pedigree data frame.
